Name: Sarah

Age: 32

Occupation: Marketing Manager

Location: Urban area

Education: Bachelor's degree in marketing

Goals: Sarah wants a hassle-free package pickup experience that is both secure and convenient. She wants to be able to pick up her packages at a time that suits her schedule without having to worry about package theft or loss. She values a service that is easy to use and provides clear communication channels for customer support.

Challenges: Sarah's work schedule is often unpredictable, which makes it difficult for her to be available during delivery hours. She may also have limited access to a car, which can make it challenging to pick up packages from a centralized location. Additionally, she is concerned about package theft, as she lives in an urban area where package theft is common.

Technology use: Sarah is tech-savvy and frequently uses her smartphone and computer for work and personal tasks. She prefers digital communication and services that are user-friendly and easy to use. She is comfortable using online payment systems and has experience using self-service applications.

Based on Sarah's persona, we can design the self-service parcel pickup service and web application to meet her needs by providing a secure, flexible, and user-friendly experience. This may include features such as:
\begin{itemize}
    \item Real-time updates on package status and locker availability
    \item Clear communication channels for customer support, including online chat or email support
    \item An intuitive user interface for scheduling pickups and retrieving packages, with the ability to select a pickup time that suits Sarah's schedule
    \item Mobile optimization for easy access and a seamless user experience on smartphones
    \item Secure and easy-to-use online payment system for any additional fees or charges
    \item A convenient and accessible pickup location, such as a locker located near Sarah's home or workplace
    \item Measures to ensure package security, such as video surveillance and secure access codes for locker retrieval
\end{itemize}
