\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{lipsum}

\begin{document}
Name: John

Age: 68

Occupation: Retired

Location: Suburban

Education: Bachelor's degree in business

Goals: John wants a reliable and easy-to-use package pickup service that allows him to receive packages from his adult children living abroad. He values flexibility and convenience, as he may have limited mobility due to age-related health issues. Additionally, he wants a service that is easy to use and provides clear communication channels for customer support.

Challenges: John may have limited mobility due to age-related health issues, which can make it difficult for him to travel to centralized package pickup locations. Additionally, he may have limited experience using digital technology, which can make it challenging to navigate the self-service pickup process. Finally, he may also be concerned about package theft, as he lives in an area where package theft is common.

Technology use: John has some experience using digital technology, including email and basic internet browsing. However, he may not be comfortable using more advanced features or self-service applications. He prefers services that are user-friendly and straightforward.

Based on John's persona, we can design the self-service parcel pickup service and web application to meet his needs by providing a reliable, convenient, and user-friendly experience. This may include features such as:
\begin{itemize}
    \item A dedicated customer support team to assist John with any questions or issues he may have
    \item An intuitive user interface for scheduling pickups and retrieving packages, with clear and simple instructions
    \item A convenient and accessible pickup location, such as a locker located near John's home or workplace, with the ability to request home delivery if needed
    \item Mobile optimization for easy access and a seamless user experience on smartphones or tablets, with clear and simple instructions for use
    \item Measures to ensure package security, such as video surveillance and secure access codes for locker retrieval, with clear and simple instructions for use
\end{itemize}

\end{document}